\bibliographystyle{IEEEtranN}
\begin{thebibliography}{27}

\bibitem{1} Benjamin Erb , Jan-Patrick Elsholz and Franz J. Hauck \emph{``Semantic Mashup: Mashing up the information in Today's World Wide Web - An Overview''}, Technical Report Document Number: VS-R08-2009  Institute for Distributed Systems, University of Ulm, 2009

\bibitem{2} Mashup, http://en.wikipedia.org/wiki/Mashup\_(web\_application\_hybrid)

\bibitem{3} Future Generation Communication and Networking Symposia, International Conference on, Vol. 2 (2008), pp. 50-53, doi:10.1109/FGCNS.2008.73

\bibitem{4} D. Merill \emph{``Mashups: the new breed of web app''}, IBM Web Architecture Technical Library (2006)

\bibitem{5} mechanize, http://wwwsearch.sourceforge.net/mechanize/

\bibitem{6} Beautiful Soup, http://www.crummy.com/software/BeautifulSoup/bs4/doc/

\bibitem{7} In IUI '08: Proceedings of the 13th international conference on Intelligent user interfaces (2008), pp. 139-148, doi:10.1145/1378773.1378792

\bibitem{8} Nan Zang, Mary R. Bosson, Vincent Nasser. \emph{``Mashups: who? what? why?''} In CHI '08 extended abstracts on Human factors in computing systems (2008), pp. 3171-3176, doi:10.1145/1358628.1358826

\bibitem{9} Focused crawler, http://en.wikipedia.org/wiki/Focused\_crawler

\bibitem{10} isbnnetinclj (to find online prices of books in india), https://github.com/swaroopch/isbnnetinclj

\bibitem{11} Jin Yu, Boualem Bentallah, Fabio Casati, Florian Daniel. \emph{``Understanding mashup development''} IEEE Internet Computing In Internet Computing, IEEE, Vol. 12, No. 5. (09 September 2008), pp. 44-52, doi:10.1109/MIC.2008.114

\bibitem{12} Alfredo Alba, Varun Bhagwan, Tyrone Grandison. \emph{''Accessing the deep Web''} Commun. ACM, Vol. 50, No. 5. (May 2007), pp. 94-101, doi:10.1145/1230819.1241670

 \bibitem{13} R. J. Ennals \& M. N. Garofalakis (2007). \emph{``MashMaker: mashups for the masses''}. In SIGMOD'07: Proceedings of the 2007 ACM SIGMOD international conference on Management of data,pp. 1116-1118, New York, NY, USA. ACM..

\bibitem{14} R. Tuchinda, et al. (2008). \emph{``Building Mashups by example''}. In IUI '08: Proceedings of the
  13th international conference on Intelligent user interfaces, pp. 139-148, New York, NY, USA.
  ACM.

\bibitem{15} Klocker,Christoph. \emph{``Mashups : A new concept in web application programming''}. Saarbrucken:VDM Verlag Dr.Muller,2008.

\bibitem{16} N. Kulathuramaiyer (2007). \emph{``Mashups: Emerging Application Development Paradigm for a Digital Journal''}. Journal of Universal Computer Science 13(4).

\bibitem{17} R. Floyd, et al. (2007). \emph{``Web Mash-ups and Patchwork Prototyping: User-driven technological innovation with Web 2.0 and Open Source Software''}. In HICSS '07: Proceedings  of the 40th Annual Hawaii International Conference on System Sciences, Washington, DC, USA. IEEE Computer Society.

\bibitem{18} Hye-Jin Jin; Hong-Chul Lee; , \emph{``Web services development methodology using the mashup  technology''}, Smart Manufacturing Application, 2008. ICSMA 2008. International Conference on, vol., no., pp.559-562, 9-11 April 2008.

\bibitem{19} Nan Zang, \emph{``Mashups for the web-active user''}, vlhcc, pp.276-277, 2008 IEEE Symposium onVisual Languages and Human-Centric Computing, 2008.

\bibitem{20} System Usability Scale. http://en.wikipedia.org/wiki/System_usability_scale

\bibitem{21} ICN '07 Proceedings of the Sixth International Conference on Networking
  Page 32

\bibitem{22} Wong, Jeffrey and Hong, Jason I., \emph{``Making Mashups with Marmite: Towards End-User Programming for the Web''} (2007). Human-Computer Interaction Institute. Paper 65.
  http://repository.cmu.edu/hcii/65

\bibitem{23} Programmable Web. http://www.programmableweb.com/

\bibitem{24} Flask. http://flask.pocoo.org/

\bibitem{25} Yahoo pipes. http://pipes.yahoo.com/pipes/

\bibitem{26} Microsoft popfly. http://www.popfly.ms/microsoft-popfly/

\bibitem{27} Usability testing with 5 users. http://www.useit.com/alertbox/20000319.html

\end{thebibliography}

